Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-08 manuscript/manuscript.tex
edits

\Section{Materials and Methods}

\subsection{Datasets Analyzed}

\subsection{Partitioning Unique and Shared Selection Effects}

\subsection{Variance and Covariance Estimates}

We calculate the variance-covariance matrix of allele frequency changes using a
Python software package we have written, available at
\url{http://github.com/vsbuffalo/cvtk}. Our method uses the sampling depth and
number of diploid individuals sampled to correct the bias in the variance
estimates and a bias that occurs in covariance estimates between adjacent
timepoints (see Supplementary Material Sections \ref{supp:ind-depth-var-corr},
\ref{supp:cov-corr}, and \ref{supp:matrix-correction} for mathematical details
of these estimators).

\subsection{Block Bootstrap}

Throughout the paper, we make use of a block-bootstrapping procedure to

>>>>

% \Section{Materials and Methods}

% \subsection{Datasets Analyzed}

% \subsection{Partitioning Unique and Shared Selection Effects}

% We can partition the allele frequency change between the two timepoints (20
% generations) for a Longshanks line as \vb{$\Delta p_{t,\mathrm{LS1}} =
% \Delta_{_{D}} p_{t,\mathrm{LS1}} + \Delta_{_{U}} p_{t,\mathrm{LS1}} +
% \Delta_{_S} p_{t,\mathrm{LS}}$} where these  terms in are the decomposition are
% the allele frequency change due to drift in \vb{Longshanks replicate 1
%   ($\Delta_{_D} p_{t,\mathrm{LS1}}$), selection unique to the LS1 replicate
%   ($\Delta_{_U} p_{t,\mathrm{LS1}}$), and selection response shared between the
% two Longshanks replicates ($\Delta_{_S} p_{t,\mathrm{LS}}$) respectively (and
% similarly for the Longshanks two line, LS2)}. By construction we will assume
% that each of these terms are uncorrelated within replicates, and that only the
% shared term covaries between the replicates. Assuming that we can approximate
% the contribution of genetic drift in the LS lines the variance in allele
% frequency change observed in the control, i.e. \vb{$\var(\Delta
% p_{t,\mathrm{Ctrl}}) = \var(\Delta_{_{D}}
% p_{t,\mathrm{LS2}})=\var(\Delta_{_{D}} p_{t,\mathrm{LS2}})$}, then we can
% estimate the increase in variance in allele frequency change due to selection
% as $(\var(\Delta p_{t,\mathrm{LS1}}) + \var(\Delta p_{t,\mathrm{LS2}}))/2 -
% \var(\Delta p_{t,\mathrm{Ctrl}})$ and the shared effect of selection across
% selected lines as $\cov(\Delta p_{t,\mathrm{LS1}}, \Delta p_{t,\mathrm{LS2}})$.

% \subsection{Variance and Covariance Estimates}

% We calculate the variance-covariance matrix of allele frequency changes using a
% Python software package we have written, available at
% \url{http://github.com/vsbuffalo/cvtk}. Our method uses the sampling depth and
% number of diploid individuals sampled to correct the bias in the variance
% estimates and a bias that occurs in covariance estimates between adjacent
% timepoints (see Supplementary Material Sections \ref{supp:ind-depth-var-corr},
% \ref{supp:cov-corr}, and \ref{supp:matrix-correction} for mathematical details
% of these estimators).

% \subsection{Block Bootstrap}
